---
title: "CellxGene Replication: Cell Density vs Metabolic Rate"
subtitle: "Validation of Hanson/Karlsen/Morgan findings using Whole Human Brain Atlas"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8
)

library(ggplot2)
library(ggrepel)
library(patchwork)
library(knitr)
library(car)
library(dplyr)
```

# Background

This analysis replicates the findings from Hanson et al. (2018), Karlsen & Pakkenberg (2011), and Morgan et al. (2014) using **NEW data from the Whole Human Brain Atlas** via CellxGene.

**Original findings:**
- Astrocyte density: r = 0.968, p = .002
- Oligodendrocyte density: r = 0.897, p = .016
- Microglia density: r = 0.937, p = .006
- Total glia density: r = 0.708, p = .075 (NS)

# Load CellxGene Data

```{r load-data}
# Set working directory
setwd("C:\\Users\\michaelproulx\\Downloads\\1A analyses metabol rates regions\\1A analyses metabol rates regions\\R")

# Load CellxGene data (now relative to working directory)
cellxgene_data <- read.csv(
  "cellxgene_integration\\ei_analysis\\data\\cortical\\followup_analyses\\subregions_with_cell_composition.csv",
  header = TRUE
)

# Display summary
cat("=== CELLXGENE DATA SUMMARY ===\n")
cat("Number of cortical subregions:", nrow(cellxgene_data), "\n")
cat("Regions:", paste(cellxgene_data$Region, collapse=", "), "\n\n")

# Show first few rows
kable(head(cellxgene_data[, c("Region", "Lobe", "rCMRGlc_Mean", "Total_Neuron",
                               "Astrocyte", "Oligodendrocyte", "Microglia", "Total_Glia")]),
      caption = "CellxGene Cell Composition Data (First 6 Regions)")
```

# Calculate Densities

Since CellxGene provides cell counts, we need to calculate densities.
We'll express as proportions (cells per 10,000 total cells) to match the concept of "density."

```{r calculate-densities}
# Calculate cell densities as proportions
cellxgene_data$Total_Cells_All <- cellxgene_data$Total_Neuron + cellxgene_data$Total_Glia

# Densities per 10,000 cells
cellxgene_data$Neuron_Density <- (cellxgene_data$Total_Neuron / cellxgene_data$Total_Cells_All) * 10000
cellxgene_data$Glia_Density <- (cellxgene_data$Total_Glia / cellxgene_data$Total_Cells_All) * 10000
cellxgene_data$Astrocyte_Density <- (cellxgene_data$Astrocyte / cellxgene_data$Total_Cells_All) * 10000
cellxgene_data$Oligodendrocyte_Density <- (cellxgene_data$Oligodendrocyte / cellxgene_data$Total_Cells_All) * 10000
cellxgene_data$Microglia_Density <- (cellxgene_data$Microglia / cellxgene_data$Total_Cells_All) * 10000
cellxgene_data$GliaNeuron_Ratio <- cellxgene_data$Glia_Density / cellxgene_data$Neuron_Density

# Show calculated densities
kable(head(cellxgene_data[, c("Region", "rCMRGlc_Mean", "Neuron_Density", "Glia_Density",
                               "Astrocyte_Density", "Oligodendrocyte_Density", "Microglia_Density")]),
      caption = "Calculated Cell Densities (per 10,000 cells)",
      digits = 2)
```

# Aggregate by Lobe

To better match the original analysis (which used lobes), let's aggregate to lobe level.

```{r aggregate-lobes}
library(dplyr)

# Aggregate to lobe level (weighted by total cells)
lobe_data <- cellxgene_data %>%
  group_by(Lobe) %>%
  summarise(
    rCMRGlc_Mean = first(rCMRGlc_Mean),  # Same within lobe
    n_regions = n(),

    # Sum counts
    Total_Neuron = sum(Total_Neuron),
    Total_Glia = sum(Total_Glia),
    Astrocyte = sum(Astrocyte),
    Oligodendrocyte = sum(Oligodendrocyte),
    Microglia = sum(Microglia),
    Total_Cells = sum(Total_Cells_All),

    .groups = 'drop'
  ) %>%
  mutate(
    # Calculate densities per 10,000 cells
    Neuron_Density = (Total_Neuron / Total_Cells) * 10000,
    Glia_Density = (Total_Glia / Total_Cells) * 10000,
    Astrocyte_Density = (Astrocyte / Total_Cells) * 10000,
    Oligodendrocyte_Density = (Oligodendrocyte / Total_Cells) * 10000,
    Microglia_Density = (Microglia / Total_Cells) * 10000,
    GliaNeuron_Ratio = Glia_Density / Neuron_Density
  )

cat("\n=== LOBE-LEVEL DATA ===\n")
print(lobe_data)

kable(lobe_data[, c("Lobe", "rCMRGlc_Mean", "n_regions", "Neuron_Density", "Glia_Density",
                    "Astrocyte_Density", "Oligodendrocyte_Density", "Microglia_Density")],
      caption = "Lobe-Level Aggregated Densities",
      digits = 2)
```

# Replication Analysis: Lobe Level

```{r lobe-correlations}
cat("\n=== LOBE-LEVEL CORRELATIONS WITH rCMRGlc ===\n\n")

# Function to test correlation
test_correlation <- function(data, var_name, label) {
  valid_data <- data[!is.na(data[[var_name]]) & !is.na(data$rCMRGlc_Mean), ]

  if (nrow(valid_data) >= 3) {
    cor_test <- cor.test(valid_data$rCMRGlc_Mean, valid_data[[var_name]])
    lm_model <- lm(as.formula(paste(var_name, "~ rCMRGlc_Mean")), data = valid_data)
    lm_sum <- summary(lm_model)

    cat(sprintf("%s:\n", label))
    cat(sprintf("  n = %d\n", nrow(valid_data)))
    cat(sprintf("  r = %.3f\n", cor_test$estimate))
    cat(sprintf("  p-value = %.4f %s\n", cor_test$p.value,
                ifelse(cor_test$p.value < 0.05, "***", "")))
    cat(sprintf("  95%% CI: [%.3f, %.3f]\n", cor_test$conf.int[1], cor_test$conf.int[2]))
    cat(sprintf("  R² = %.3f\n", lm_sum$r.squared))
    cat(sprintf("  Beta = %.2e, t = %.3f\n\n", coef(lm_model)[2], lm_sum$coefficients[2, 3]))

    return(list(
      var = var_name,
      label = label,
      n = nrow(valid_data),
      r = cor_test$estimate,
      p = cor_test$p.value,
      ci_lower = cor_test$conf.int[1],
      ci_upper = cor_test$conf.int[2],
      r_squared = lm_sum$r.squared,
      beta = coef(lm_model)[2]
    ))
  }
}

# Test all densities
results_lobe <- list(
  test_correlation(lobe_data, "Neuron_Density", "Neuron Density"),
  test_correlation(lobe_data, "Glia_Density", "Total Glia Density"),
  test_correlation(lobe_data, "Astrocyte_Density", "Astrocyte Density"),
  test_correlation(lobe_data, "Oligodendrocyte_Density", "Oligodendrocyte Density"),
  test_correlation(lobe_data, "Microglia_Density", "Microglia Density"),
  test_correlation(lobe_data, "GliaNeuron_Ratio", "Glia:Neuron Ratio")
)

# Create summary table
results_df_lobe <- do.call(rbind, lapply(results_lobe, as.data.frame))
results_df_lobe <- results_df_lobe[order(results_df_lobe$p), ]

kable(results_df_lobe,
      caption = "Lobe-Level Correlation Summary (sorted by p-value)",
      digits = 4)
```

# Replication Analysis: Subregion Level

```{r subregion-correlations}
cat("\n=== SUBREGION-LEVEL CORRELATIONS WITH rCMRGlc ===\n\n")

# Test all densities at subregion level
results_subregion <- list(
  test_correlation(cellxgene_data, "Neuron_Density", "Neuron Density"),
  test_correlation(cellxgene_data, "Glia_Density", "Total Glia Density"),
  test_correlation(cellxgene_data, "Astrocyte_Density", "Astrocyte Density"),
  test_correlation(cellxgene_data, "Oligodendrocyte_Density", "Oligodendrocyte Density"),
  test_correlation(cellxgene_data, "Microglia_Density", "Microglia Density"),
  test_correlation(cellxgene_data, "GliaNeuron_Ratio", "Glia:Neuron Ratio")
)

# Create summary table
results_df_subregion <- do.call(rbind, lapply(results_subregion, as.data.frame))
results_df_subregion <- results_df_subregion[order(results_df_subregion$p), ]

kable(results_df_subregion,
      caption = "Subregion-Level Correlation Summary (sorted by p-value)",
      digits = 4)
```

# Visualization: Glial Subtypes (Lobe Level)

```{r plot-lobe-subtypes, fig.width=14, fig.height=10}
cb_palette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
                "#0072B2", "#D55E00", "#CC79A7", "#999999")

# Create plots for each glial subtype
plot_list <- list()

for (i in 1:3) {
  var_info <- list(
    list(var = "Astrocyte_Density", label = "Astrocyte Density", color = 1),
    list(var = "Oligodendrocyte_Density", label = "Oligodendrocyte Density", color = 2),
    list(var = "Microglia_Density", label = "Microglia Density", color = 3)
  )[[i]]

  cor_test <- cor.test(lobe_data$rCMRGlc_Mean, lobe_data[[var_info$var]])

  p <- ggplot(lobe_data, aes(x = rCMRGlc_Mean, y = .data[[var_info$var]])) +
    geom_point(size = 4, color = cb_palette[var_info$color], alpha = 0.8) +
    geom_smooth(method = "lm", color = cb_palette[var_info$color+1],
                fill = cb_palette[var_info$color+1], alpha = 0.2, linewidth = 1.2) +
    geom_text_repel(aes(label = Lobe), size = 3.5, box.padding = 0.5) +
    labs(title = var_info$label,
         subtitle = sprintf("r = %.3f, p = %.4f, n = %d lobes",
                          cor_test$estimate, cor_test$p.value, nrow(lobe_data)),
         x = "rCMRGlc (µmol/100g/min)",
         y = paste(var_info$label, "(per 10,000 cells)")) +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 14),
      plot.subtitle = element_text(size = 11),
      axis.title = element_text(face = "bold")
    )

  plot_list[[i]] <- p
}

# Add total glia plot
cor_test <- cor.test(lobe_data$rCMRGlc_Mean, lobe_data$Glia_Density)
p <- ggplot(lobe_data, aes(x = rCMRGlc_Mean, y = Glia_Density)) +
  geom_point(size = 4, color = cb_palette[4], alpha = 0.8) +
  geom_smooth(method = "lm", color = cb_palette[5],
              fill = cb_palette[5], alpha = 0.2, linewidth = 1.2) +
  geom_text_repel(aes(label = Lobe), size = 3.5, box.padding = 0.5) +
  labs(title = "Total Glia Density",
       subtitle = sprintf("r = %.3f, p = %.4f, n = %d lobes",
                        cor_test$estimate, cor_test$p.value, nrow(lobe_data)),
       x = "rCMRGlc (µmol/100g/min)",
       y = "Total Glia Density (per 10,000 cells)") +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 11),
    axis.title = element_text(face = "bold")
  )

plot_list[[4]] <- p

# Combine plots
combined <- wrap_plots(plot_list, ncol = 2) +
  plot_annotation(
    title = "CellxGene Replication: Glial Cell Densities vs Metabolic Rate (Lobe Level)",
    subtitle = "Whole Human Brain Atlas Data",
    theme = theme(plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
                  plot.subtitle = element_text(size = 12, hjust = 0.5))
  )

print(combined)
ggsave("CellxGene_Lobe_Glia_Replication.png", combined,
       width = 14, height = 10, dpi = 300, bg = "white")
```

# Visualization: Glial Subtypes (Subregion Level)

```{r plot-subregion-subtypes, fig.width=14, fig.height=10}
# Create plots for each glial subtype at subregion level
plot_list_sub <- list()

for (i in 1:3) {
  var_info <- list(
    list(var = "Astrocyte_Density", label = "Astrocyte Density", color = 1),
    list(var = "Oligodendrocyte_Density", label = "Oligodendrocyte Density", color = 2),
    list(var = "Microglia_Density", label = "Microglia Density", color = 3)
  )[[i]]

  cor_test <- cor.test(cellxgene_data$rCMRGlc_Mean, cellxgene_data[[var_info$var]])

  p <- ggplot(cellxgene_data, aes(x = rCMRGlc_Mean, y = .data[[var_info$var]])) +
    geom_point(size = 3, color = cb_palette[var_info$color], alpha = 0.8) +
    geom_smooth(method = "lm", color = cb_palette[var_info$color+1],
                fill = cb_palette[var_info$color+1], alpha = 0.2, linewidth = 1.2) +
    geom_text_repel(aes(label = Region), size = 2.5, box.padding = 0.3, max.overlaps = 15) +
    labs(title = var_info$label,
         subtitle = sprintf("r = %.3f, p = %.4f, n = %d regions",
                          cor_test$estimate, cor_test$p.value, nrow(cellxgene_data)),
         x = "rCMRGlc",
         y = paste(var_info$label, "(per 10k cells)")) +
    theme_minimal(base_size = 11) +
    theme(
      plot.title = element_text(face = "bold", size = 12),
      plot.subtitle = element_text(size = 10)
    )

  plot_list_sub[[i]] <- p
}

# Add total glia plot
cor_test <- cor.test(cellxgene_data$rCMRGlc_Mean, cellxgene_data$Glia_Density)
p <- ggplot(cellxgene_data, aes(x = rCMRGlc_Mean, y = Glia_Density)) +
  geom_point(size = 3, color = cb_palette[4], alpha = 0.8) +
  geom_smooth(method = "lm", color = cb_palette[5],
              fill = cb_palette[5], alpha = 0.2, linewidth = 1.2) +
  geom_text_repel(aes(label = Region), size = 2.5, box.padding = 0.3, max.overlaps = 15) +
  labs(title = "Total Glia Density",
       subtitle = sprintf("r = %.3f, p = %.4f, n = %d regions",
                        cor_test$estimate, cor_test$p.value, nrow(cellxgene_data)),
       x = "rCMRGlc",
       y = "Total Glia Density (per 10k cells)") +
  theme_minimal(base_size = 11) +
  theme(
    plot.title = element_text(face = "bold", size = 12),
    plot.subtitle = element_text(size = 10)
  )

plot_list_sub[[4]] <- p

# Combine plots
combined_sub <- wrap_plots(plot_list_sub, ncol = 2) +
  plot_annotation(
    title = "CellxGene Replication: Glial Cell Densities vs Metabolic Rate (Subregion Level)",
    subtitle = "Whole Human Brain Atlas Data (21 cortical regions)",
    theme = theme(plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
                  plot.subtitle = element_text(size = 12, hjust = 0.5))
  )

print(combined_sub)
ggsave("CellxGene_Subregion_Glia_Replication.png", combined_sub,
       width = 14, height = 10, dpi = 300, bg = "white")
```

# Comparison with Original Results

```{r comparison}
cat("\n", strrep("=", 80), "\n")
cat("COMPARISON: ORIGINAL vs CELLXGENE REPLICATION\n")
cat(strrep("=", 80), "\n\n")

# Original results
original <- data.frame(
  Variable = c("Astrocyte Density", "Oligodendrocyte Density", "Microglia Density", "Total Glia Density"),
  Original_r = c(0.968, 0.897, 0.937, 0.708),
  Original_p = c(0.002, 0.016, 0.006, 0.075),
  Original_n = c(6, 6, 6, 7),
  Source = c("Hanson/Karlsen/Morgan", "Hanson/Karlsen/Morgan", "Hanson/Karlsen/Morgan", "Hanson/Karlsen/Morgan")
)

# Get CellxGene lobe-level results
cellxgene_lobe <- data.frame(
  Variable = results_df_lobe$label,
  CellxGene_Lobe_r = results_df_lobe$r,
  CellxGene_Lobe_p = results_df_lobe$p,
  CellxGene_Lobe_n = results_df_lobe$n
)

# Get CellxGene subregion-level results
cellxgene_sub <- data.frame(
  Variable = results_df_subregion$label,
  CellxGene_Sub_r = results_df_subregion$r,
  CellxGene_Sub_p = results_df_subregion$p,
  CellxGene_Sub_n = results_df_subregion$n
)

# Merge for comparison
comparison <- merge(original, cellxgene_lobe, by = "Variable", all.x = TRUE)
comparison <- merge(comparison, cellxgene_sub, by = "Variable", all.x = TRUE)

# Add significance markers
comparison$Original_Sig <- ifelse(comparison$Original_p < 0.05, "***", "")
comparison$Lobe_Sig <- ifelse(comparison$CellxGene_Lobe_p < 0.05, "***", "")
comparison$Sub_Sig <- ifelse(comparison$CellxGene_Sub_p < 0.05, "***", "")

kable(comparison,
      caption = "Comparison of Original Results with CellxGene Replication",
      digits = 4)

cat("\n=== INTERPRETATION ===\n\n")
cat("The CellxGene data provides an independent validation of the original findings:\n\n")

if (any(cellxgene_lobe$CellxGene_Lobe_p[1:3] < 0.05)) {
  cat("✓ REPLICATED: Glial subtype densities show relationships with rCMRGlc\n")
} else {
  cat("✗ NOT REPLICATED: Glial subtype densities do not show significant relationships\n")
}

if (cellxgene_lobe$CellxGene_Lobe_p[cellxgene_lobe$Variable == "Total Glia Density"] >= 0.05) {
  cat("✓ CONFIRMED: Total glia density remains non-significant (consistent with original)\n")
} else {
  cat("✗ DIFFERENT: Total glia density IS significant in CellxGene data\n")
}

cat("\n", strrep("=", 80), "\n")
```

# Summary

```{r summary}
cat("\n=== ANALYSIS COMPLETE ===\n\n")

cat("FILES CREATED:\n")
cat("- CellxGene_Lobe_Glia_Replication.png\n")
cat("- CellxGene_Subregion_Glia_Replication.png\n\n")

cat("This analysis used single-cell RNA-seq data from the Whole Human Brain Atlas\n")
cat("(CellxGene) to independently validate findings from traditional histology studies.\n\n")

cat("Sample size comparison:\n")
cat("- Original: 6-7 brain regions from 3 papers\n")
cat("- CellxGene Lobe: 5 lobes\n")
cat("- CellxGene Subregion: 21 cortical subregions\n\n")
```

# Session Info

```{r}
sessionInfo()
```
