## Install and Load up packages
```{r}
library(here)
library(ape)
library(geiger)
library(nlme)
library(caper)
library(car)
library(ggplot2)
library(ggrepel)
library(patchwork)
```

# Paths relative to project root:
```{r}
r_dir      <- here("R")
data_dir   <- here("data")
output_dir <- here("output")
```

# PART 2: Brain Structure Metabolic Rates (rCMRGlc) compared to Anatomical Variables

## Preparation

### Load data
```{r}
MetaData <- read.csv(here("data", "brain_struct_metabol_anat.csv"), header = TRUE)
```

## Regressions

# Fixed # Regression x = rCMRGlc y = slope
```{r}
lm.slope <- lm(slope ~ rCMRGlc, data = MetaData)
summary(lm.slope)
plot(MetaData$rCMRGlc, MetaData$slope,
     pch = 16, cex = 1.3, col = "blue",
     main = "slope as a function of rCMRGlc",
     xlab = "rCMRGlc", ylab = "Slope")
abline(lm.slope)
```

# Regression x = rCMRGlc y = lambda
```{r}
lm.lambda <- lm(lambda ~ rCMRGlc, data = MetaData)
summary(lm.lambda)
```

# Regression x = rCMRGlc y = OP_Diff
```{r}
lm.OP_Diff <- lm(OP_Diff ~ rCMRGlc, data = MetaData)
summary(lm.OP_Diff)
```

# Regression x = rCMRGlc y = aging_Beta
```{r}
lm.aging_Beta <- lm(aging_Beta ~ rCMRGlc, data = MetaData)
summary(lm.aging_Beta)
```

# Regression x = rCMRGlc y = aging_change
```{r}
lm.aging_change <- lm(aging_change ~ rCMRGlc, data = MetaData)
summary(lm.aging_change)
```

# Regression x = rCMRGlc y = development_change
```{r}
lm.development_change <- lm(development_change ~ rCMRGlc, data = MetaData)
summary(lm.development_change)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = development_change
```{r}
crf.lm.development_change <- lm(development_change ~ rCMRGlc, data = MetaData)
Anova(crf.lm.development_change, type=3)
```

# Regression x = rCMRGlc y = Orphan_change
```{r}
lm.Orphan_change <- lm(Orphan_change ~ rCMRGlc, data = MetaData)
summary(lm.Orphan_change)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = Orphan_change
```{r}
crf.lm.Orphan_change <- lm(Orphan_change ~ rCMRGlc, data = MetaData)
Anova(crf.lm.Orphan_change, type=3)
```

# NEW - Michael's fancy new regressions! Load data above.
# Regression x = rCMRGlc y = Volume
```{r}
lm.Volume <- lm(Volume ~ rCMRGlc, data = MetaData)
summary(lm.Volume)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = Volume
```{r}
crf.lm.Volume <- lm(Volume ~ rCMRGlc, data = MetaData)
Anova(crf.lm.Volume, type=3)
```

# Regression x = rCMRGlc y = VolumeSD
```{r}
lm.VolumeSD <- lm(VolumeSD ~ rCMRGlc, data = MetaData)
summary(lm.VolumeSD)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = VolumeSD
```{r}
crf.lm.VolumeSD <- lm(VolumeSD ~ rCMRGlc, data = MetaData)
Anova(crf.lm.VolumeSD, type=3)
```

# Regression x = rCMRGlc y = Neuron_N
```{r}
lm.Neuron_N <- lm(Neuron_N ~ rCMRGlc, data = MetaData)
summary(lm.Neuron_N)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = Neuron_N
```{r}
crf.lm.Neuron_N <- lm(Neuron_N ~ rCMRGlc, data = MetaData)
Anova(crf.lm.Neuron_N, type=3)
```

# Regression x = rCMRGlc y = NeuronSD
```{r}
lm.NeuronSD <- lm(NeuronSD ~ rCMRGlc, data = MetaData)
summary(lm.NeuronSD)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = NeuronSD
```{r}
crf.lm.NeuronSD <- lm(NeuronSD ~ rCMRGlc, data = MetaData)
Anova(crf.lm.NeuronSD, type=3)
```

# Regression x = rCMRGlc y = NeurDensity
```{r}
lm.NeurDensity <- lm(NeurDensity ~ rCMRGlc, data = MetaData)
summary(lm.NeurDensity)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = NeurDensity
```{r}
crf.lm.NeurDensity <- lm(NeurDensity ~ rCMRGlc, data = MetaData)
Anova(crf.lm.NeurDensity, type=3)
```

# Regression x = rCMRGlc y = Glia_N
```{r}
lm.Glia_N <- lm(Glia_N ~ rCMRGlc, data = MetaData)
summary(lm.Glia_N)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = Glia_N
```{r}
crf.lm.Glia_N <- lm(Glia_N ~ rCMRGlc, data = MetaData)
Anova(crf.lm.Glia_N, type=3)
```

# Regression x = rCMRGlc y = GliaSD
```{r}
lm.GliaSD <- lm(GliaSD ~ rCMRGlc, data = MetaData)
summary(lm.GliaSD)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = GliaSD
```{r}
crf.lm.GliaSD <- lm(GliaSD ~ rCMRGlc, data = MetaData)
Anova(crf.lm.GliaSD, type=3)
```

# Regression x = rCMRGlc y = GliaDensity
```{r}
lm.GliaDensity <- lm(GliaDensity ~ rCMRGlc, data = MetaData)
summary(lm.GliaDensity)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = GliaDensity
```{r}
crf.lm.GliaDensity <- lm(GliaDensity ~ rCMRGlc, data = MetaData)
Anova(crf.lm.GliaDensity, type=3)
```

# Regression x = rCMRGlc y = Astro_N
```{r}
lm.Astro_N <- lm(Astro_N ~ rCMRGlc, data = MetaData)
summary(lm.Astro_N)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = Astro_N
```{r}
crf.lm.Astro_N <- lm(Astro_N ~ rCMRGlc, data = MetaData)
Anova(crf.lm.Astro_N, type=3)
```

# Regression x = rCMRGlc y = AstroSD
```{r}
lm.AstroSD <- lm(AstroSD ~ rCMRGlc, data = MetaData)
summary(lm.AstroSD)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = AstroSD
```{r}
crf.lm.AstroSD <- lm(AstroSD ~ rCMRGlc, data = MetaData)
Anova(crf.lm.AstroSD, type=3)
```

# Regression x = rCMRGlc y = AstroDensity
```{r}
lm.AstroDensity <- lm(AstroDensity ~ rCMRGlc, data = MetaData)
summary(lm.AstroDensity)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = AstroDensity
```{r}
crf.lm.AstroDensity <- lm(AstroDensity ~ rCMRGlc, data = MetaData)
Anova(crf.lm.AstroDensity, type=3)
```

# Regression x = rCMRGlc y = Oligo_N
```{r}
lm.Oligo_N <- lm(Oligo_N ~ rCMRGlc, data = MetaData)
summary(lm.Oligo_N)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = Oligo_N
```{r}
crf.lm.Oligo_N <- lm(Oligo_N ~ rCMRGlc, data = MetaData)
Anova(crf.lm.Oligo_N, type=3)
```

# Regression x = rCMRGlc y = OligoSD
```{r}
lm.OligoSD <- lm(OligoSD ~ rCMRGlc, data = MetaData)
summary(lm.OligoSD)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = OligoSD
```{r}
crf.lm.OligoSD <- lm(OligoSD ~ rCMRGlc, data = MetaData)
Anova(crf.lm.OligoSD, type=3)
```

# Regression x = rCMRGlc y = OligoDensity
```{r}
lm.OligoDensity <- lm(OligoDensity ~ rCMRGlc, data = MetaData)
summary(lm.OligoDensity)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = OligoDensity
```{r}
crf.lm.OligoDensity <- lm(OligoDensity ~ rCMRGlc, data = MetaData)
Anova(crf.lm.OligoDensity, type=3)
```

# Regression x = rCMRGlc y = Microglia_N
```{r}
lm.Microglia_N <- lm(Microglia_N ~ rCMRGlc, data = MetaData)
summary(lm.Microglia_N)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = Microglia_N
```{r}
crf.lm.Microglia_N <- lm(Microglia_N ~ rCMRGlc, data = MetaData)
Anova(crf.lm.Microglia_N, type=3)
```

# Regression x = rCMRGlc y = MicroSD
```{r}
lm.MicroSD <- lm(MicroSD ~ rCMRGlc, data = MetaData)
summary(lm.MicroSD)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = MicroSD
```{r}
crf.lm.MicroSD <- lm(MicroSD ~ rCMRGlc, data = MetaData)
Anova(crf.lm.MicroSD, type=3)
```

# Regression x = rCMRGlc y = MicroDensity
```{r}
lm.MicroDensity <- lm(MicroDensity ~ rCMRGlc, data = MetaData)
summary(lm.MicroDensity)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = MicroDensity
```{r}
crf.lm.MicroDensity <- lm(MicroDensity ~ rCMRGlc, data = MetaData)
Anova(crf.lm.MicroDensity, type=3)
```

# Regression x = rCMRGlc y = GliaNeurDensityRatio
```{r}
lm.GliaNeurDensityRatio <- lm(GliaNeurDensityRatio ~ rCMRGlc, data = MetaData)
summary(lm.GliaNeurDensityRatio)
```

# SPSS style Type 3 # Regression x = rCMRGlc y = GliaNeurDensityRatio
```{r}
crf.lm.GliaNeurDensityRatio <- lm(GliaNeurDensityRatio ~ rCMRGlc, data = MetaData)
Anova(crf.lm.GliaNeurDensityRatio, type=3)
```

## MICHAEL OPTIMIZED LLM LOOP CODE
```{r}
dep_vars <- c(
  "Volume", "VolumeSD", "Neuron_N", "NeuronSD", "NeurDensity",
  "Glia_N", "GliaSD", "GliaDensity",
  "Astro_N", "AstroSD", "AstroDensity",
  "Oligo_N", "OligoSD", "OligoDensity",
  "Microglia_N", "MicroSD", "MicroDensity",
  "GliaNeurDensityRatio"
)
```

```{r}
# Prepare lists to store results
regression_results <- list()
anova_results <- list()

# Prepare a summary table
summary_table <- data.frame(
  Dependent = character(),
  Estimate = numeric(),
  StdError = numeric(),
  tValue = numeric(),
  pValue = numeric(),
  stringsAsFactors = FALSE
)

# Loop through each dependent variable
for (dv in dep_vars) {
  formula <- as.formula(paste(dv, "~ rCMRGlc"))
  model <- lm(formula, data = MetaData)
  regression_results[[dv]] <- summary(model)
  anova_results[[dv]] <- Anova(model, type = 3)

  # Extract coefficient info for summary table
  coef_info <- summary(model)$coefficients["rCMRGlc", ]
  summary_table <- rbind(summary_table, data.frame(
    Dependent = dv,
    Estimate = coef_info["Estimate"],
    StdError = coef_info["Std. Error"],
    tValue = coef_info["t value"],
    pValue = coef_info["Pr(>|t|)"]
  ))
}
```

# Display all results in console
```{r}
for (dv in dep_vars) {
  cat("\n--- Regression for", dv, "~ rCMRGlc ---\n")
  print(regression_results[[dv]])
  cat("\n--- Type III ANOVA for", dv, "~ rCMRGlc ---\n")
  print(anova_results[[dv]])
}
```

# Save summary table
```{r}
write.csv(summary_table, here("output", "regression_summary_table.csv"), row.names = FALSE)
print(summary_table)
```

# Save full results to text file
```{r}
sink(here("output", "regression_full_results.txt"))
for (dv in dep_vars) {
  cat("\n--- Regression for", dv, "~ rCMRGlc ---\n")
  print(regression_results[[dv]])
  cat("\n--- Type III ANOVA for", dv, "~ rCMRGlc ---\n")
  print(anova_results[[dv]])
}
sink()
```

# NEW: Individual Cell Type Plots (Nandita-Style)

## Create Individual Regression Plots for Each Cell Type
```{r fig.width=10, fig.height=8}
# Define cell types for individual analysis
cell_types <- list(
  Neurons = list(var = "Neuron_N", label = "Neuron Count"),
  Glia = list(var = "Glia_N", label = "Glia Count"),
  Astrocytes = list(var = "Astro_N", label = "Astrocyte Count"),
  Oligodendrocytes = list(var = "Oligo_N", label = "Oligodendrocyte Count"),
  Microglia = list(var = "Microglia_N", label = "Microglia Count"),

  NeuronDensity = list(var = "NeurDensity", label = "Neuron Density"),
  GliaDensity = list(var = "GliaDensity", label = "Glia Density"),
  AstroDensity = list(var = "AstroDensity", label = "Astrocyte Density"),
  OligoDensity = list(var = "OligoDensity", label = "Oligodendrocyte Density"),
  MicroDensity = list(var = "MicroDensity", label = "Microglia Density"),

  GliaNeurRatio = list(var = "GliaNeurDensityRatio", label = "Glia:Neuron Density Ratio")
)

# Color-blind friendly palette
cb_palette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
                "#0072B2", "#D55E00", "#CC79A7", "#999999")

# Create individual plots for each cell type
for (i in seq_along(cell_types)) {
  cell_name <- names(cell_types)[i]
  var_name <- cell_types[[i]]$var
  var_label <- cell_types[[i]]$label

  # Filter data with valid values for both variables
  plot_data <- MetaData[!is.na(MetaData[[var_name]]) &
                        !is.na(MetaData$rCMRGlc), ]

  if (nrow(plot_data) < 3) {
    cat(sprintf("\nSkipping %s - insufficient data (n=%d)\n", cell_name, nrow(plot_data)))
    next
  }

  # Run correlation test
  cor_test <- cor.test(plot_data$rCMRGlc, plot_data[[var_name]],
                       method = "pearson")

  # Run regression
  formula <- as.formula(paste(var_name, "~ rCMRGlc"))
  model <- lm(formula, data = plot_data)
  model_summary <- summary(model)

  # Print results
  cat(sprintf("\n=== %s vs rCMRGlc ===\n", var_label))
  cat(sprintf("Pearson r = %.3f\n", cor_test$estimate))
  cat(sprintf("p-value = %.4f\n", cor_test$p.value))
  cat(sprintf("95%% CI: [%.3f, %.3f]\n",
              cor_test$conf.int[1], cor_test$conf.int[2]))
  cat(sprintf("R² = %.3f\n", model_summary$r.squared))
  cat(sprintf("Regression: %s = %.2e + %.2e * rCMRGlc\n\n",
              var_label, coef(model)[1], coef(model)[2]))

  # Create plot
  p <- ggplot(plot_data, aes(x = rCMRGlc, y = .data[[var_name]])) +
    geom_point(size = 4, color = cb_palette[1], alpha = 0.8) +
    geom_smooth(method = "lm", color = cb_palette[2],
                fill = cb_palette[2], alpha = 0.2, linewidth = 1.2) +
    geom_text_repel(aes(label = Region), size = 3.5,
                    box.padding = 0.5, max.overlaps = 20) +
    labs(title = sprintf("%s vs Regional Cerebral Glucose Metabolism", var_label),
         subtitle = sprintf("r = %.3f, p = %.4f, R² = %.3f",
                          cor_test$estimate, cor_test$p.value,
                          model_summary$r.squared),
         x = "rCMRGlc (µmol/100g/min)",
         y = var_label) +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", size = 14),
      plot.subtitle = element_text(size = 11),
      axis.title = element_text(face = "bold")
    )

  # Save plot
  filename <- sprintf("CellType_%s_vs_rCMRGlc.png", cell_name)
  ggsave(here("output", filename), p, width = 10, height = 8, dpi = 300, bg = "white")

  # Display plot
  print(p)

  cat(sprintf("Saved: %s\n", filename))
}
```

## Summary Table with Correlations

```{r}
# Create comprehensive summary table
summary_correlations <- data.frame(
  CellType = character(),
  Variable = character(),
  n = integer(),
  r = numeric(),
  p_value = numeric(),
  CI_lower = numeric(),
  CI_upper = numeric(),
  R_squared = numeric(),
  Beta = numeric(),
  stringsAsFactors = FALSE
)

for (i in seq_along(cell_types)) {
  cell_name <- names(cell_types)[i]
  var_name <- cell_types[[i]]$var

  plot_data <- MetaData[!is.na(MetaData[[var_name]]) &
                        !is.na(MetaData$rCMRGlc), ]

  if (nrow(plot_data) >= 3) {
    cor_test <- cor.test(plot_data$rCMRGlc, plot_data[[var_name]])
    formula <- as.formula(paste(var_name, "~ rCMRGlc"))
    model <- lm(formula, data = plot_data)

    summary_correlations <- rbind(summary_correlations, data.frame(
      CellType = cell_name,
      Variable = var_name,
      n = nrow(plot_data),
      r = cor_test$estimate,
      p_value = cor_test$p.value,
      CI_lower = cor_test$conf.int[1],
      CI_upper = cor_test$conf.int[2],
      R_squared = summary(model)$r.squared,
      Beta = coef(model)[2]
    ))
  }
}

# Sort by p-value
summary_correlations <- summary_correlations[order(summary_correlations$p_value), ]

# Print table
print(summary_correlations)

# Save to CSV
write.csv(summary_correlations, here("output", "cell_type_correlations_summary.csv"), row.names = FALSE)
```

## Multi-panel Figure (Combined Significant Results)

```{r fig.width=14, fig.height=12}
# Create combined multi-panel figure for significant results
significant_vars <- summary_correlations[summary_correlations$p_value < 0.05, "Variable"]

if (length(significant_vars) > 0) {
  plot_list <- list()

  for (var_name in significant_vars) {
    plot_data <- MetaData[!is.na(MetaData[[var_name]]) &
                          !is.na(MetaData$rCMRGlc), ]

    cor_test <- cor.test(plot_data$rCMRGlc, plot_data[[var_name]])

    # Find the label
    var_label <- NA
    for (ct in cell_types) {
      if (ct$var == var_name) {
        var_label <- ct$label
        break
      }
    }

    p <- ggplot(plot_data, aes(x = rCMRGlc, y = .data[[var_name]])) +
      geom_point(size = 3, color = cb_palette[3], alpha = 0.8) +
      geom_smooth(method = "lm", color = cb_palette[4],
                  fill = cb_palette[4], alpha = 0.2) +
      labs(title = var_label,
           subtitle = sprintf("r = %.3f, p = %.4f",
                            cor_test$estimate, cor_test$p.value),
           x = "rCMRGlc", y = "") +
      theme_minimal(base_size = 10) +
      theme(plot.title = element_text(face = "bold", size = 11))

    plot_list[[length(plot_list) + 1]] <- p
  }

  # Combine plots
  combined <- wrap_plots(plot_list, ncol = 2)
  combined <- combined +
    plot_annotation(
      title = "Significant Cell Type Relationships with Metabolic Rate",
      theme = theme(plot.title = element_text(face = "bold", size = 14, hjust = 0.5))
    )

  print(combined)
  ggsave(here("output", "Combined_Significant_CellTypes.png"), combined,
         width = 14, height = 12, dpi = 300, bg = "white")

  cat("\nSaved: Combined_Significant_CellTypes.png\n")
} else {
  cat("\nNo significant relationships found (p < 0.05)\n")
}
```

## Summary
```{r}
cat("\n", strrep("=", 80), "\n")
cat("ANALYSIS COMPLETE\n")
cat(strrep("=", 80), "\n\n")

cat("FILES CREATED:\n")
cat("- regression_summary_table.csv (all 18 regressions)\n")
cat("- regression_full_results.txt (detailed output)\n")
cat("- cell_type_correlations_summary.csv (correlation summary)\n")
cat("- CellType_*.png (11 individual plots)\n")
cat("- Combined_Significant_CellTypes.png (multi-panel figure)\n\n")

cat("SIGNIFICANT RESULTS (p < 0.05):\n")
sig_results <- summary_correlations[summary_correlations$p_value < 0.05, ]
if (nrow(sig_results) > 0) {
  for (i in 1:nrow(sig_results)) {
    cat(sprintf("  %s: r = %.3f, p = %.4f\n",
                sig_results$CellType[i],
                sig_results$r[i],
                sig_results$p_value[i]))
  }
} else {
  cat("  None\n")
}

cat("\n", strrep("=", 80), "\n")
```
